This ReadMe explains the approach taken towards completing the Course Project for the Getting Clean Data Coursera course. 

run_analysis.R is the script that contains the code that analyses the UCI HAR Samsung Data and outputs a tidy data set as per Requirement 5 of the Course project. 

The following conditions are assumed as pre-requisites for the script to run successfully:
------------------------------------------------------------------------------------------

1. The current workspace is set inside the UCI-HAR-Dataset folder. E.g. D:/SamsungData/UCI-HAR-Dataset 
2. The dplyr package has been installed. This can be done using the install.packages("dplyr")

The Script routine consists of:
-------------------------------

1. The training and test data sets are loaded from the files. 
2. The features data which consists of the various kinds of measurements is loaded.
3. The names of the columns of the xtest and xtrain datasets is mapped to the features data.
4. The activity labels which consists of the kind of activities performed in the experiment is loaded.
5. The levels of the activity labels is specified in the correct order and with descriptive labels.
6. The ytest and ytrain data is coerced as a factor. The levels of these factors are mapped to the activity labels factor. 
7. The names of the ytest and ytrain are appropriately named as "Activity"
8, The xtest and ytest data is combined to form one dataframe. Similar action is performed on the training dataset.
9. The Subject data for both the training and test datasets is loaded and combined with the respective data frames.
10. The training and test datasets are merged using the rbind command.
11. The unwanted columns are removed by searching for only the column names containing the mean or std string.
12. The column names are rationalized using the make.names function to make them compatible with R.
13. Lastly, the tidy data set with the averages calculated for the measurements is generated. 

Justification that the data is tidy:
------------------------------------



```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
